---
title: "The FORRT Library of Reproduction and Replication Attempts: Documenting the Reproducibility and Replicability of the Sciences and Humanities"
author:
  - name: "Author Name"
    orcid: "0000-0000-0000-0000"
    affiliations:
      - name: "Affiliation"
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    number-sections: false
    theme: cosmo
    css: styles.css
    fig-cap-location: bottom
    tbl-cap-location: top
    code-fold: true
    code-tools: false
    embed-resources: false
    citations-hover: true
    crossrefs-hover: true
    link-external-newwindow: true
bibliography: references.bib
csl: apa.csl
link-citations: true
nocite: |
  @wallrich2026flora, @roseler2024replication, @roseler2025r2editorial
abstract: |
  *To be written.* This abstract will summarize the report's aims, methods, key
  findings, and contributions to open science. (Canonical version in
  sections/abstract.md — copy here after editing.)
execute:
  echo: false
  warning: false
  message: false
  cache: false
---

<!-- WIP ribbon -->
<div class="wip-ribbon"><span>Work in Progress</span></div>

```{r setup}
#| include: false

library(tidyverse)
library(knitr)
library(here)

flora_path <- here::here("data", "flora.csv")

if (file.exists(flora_path)) {
  flora <- readr::read_csv(flora_path, show_col_types = FALSE, na = c("", "NA"))
  data_available <- TRUE
} else {
  flora <- tibble()
  data_available <- FALSE
}

report_date <- format(Sys.Date(), "%B %d, %Y")
n_entries   <- nrow(flora)
```

::: {.callout-note appearance="simple"}
This report is automatically updated daily at 07:00 CEST using the most recent
version of the FLoRA dataset. Last build: **`r format(Sys.time(), "%Y-%m-%d %H:%M %Z")`**.
`r if (data_available) paste0("Current snapshot: **", scales::comma(n_entries), " entries**.") else "⚠ Data file not found — plots and tables are skipped in this build."`
:::

::: {.flora-box}
**Keywords:** replication, reproduction, meta-science, open science, FLoRA, FORRT
:::

::: {.flora-box}
### Lay Summary {.box-title}

{{< include sections/lay-summary.md >}}
:::

::: {.flora-box}
### Citation {.box-title}

Please cite this report as:

[Author]. (`r format(Sys.Date(), "%Y")`). *The FORRT Library of Reproduction
and Replication Attempts: Documenting the Reproducibility and Replicability of
the Sciences and Humanities.* [URL]

And cite the underlying dataset as @wallrich2026flora.
:::

<!-- ============================================================= -->
<!-- PROSE SECTIONS — edit the .md files in sections/, not here.    -->
<!-- ============================================================= -->

{{< include sections/theory.md >}}

{{< include sections/methods.md >}}

<!-- Results: prose comes from the include, R chunks live here -->

# Results {#sec-results}

*To be written.* Descriptive statistics and visualisations of the current FLoRA
snapshot.

## Overview of the Current Database

```{r}
#| label: tbl-overview
#| tbl-cap: "Overview of the current FLoRA snapshot."
#| eval: !expr data_available

flora_summary <- flora |>
  summarise(
    `Total entries`              = n(),
    `Unique original studies`    = n_distinct(doi_o, na.rm = TRUE),
    `Unique replication studies`  = n_distinct(doi_r, na.rm = TRUE),
    Replications                 = sum(type == "replication", na.rm = TRUE),
    Reproductions                = sum(type == "reproduction", na.rm = TRUE)
  ) |>
  pivot_longer(everything(), names_to = "Category", values_to = "Count")

knitr::kable(flora_summary, format = "html")
```

## Replication Attempts

### Replications Across Disciplines

*To be written.*

### Replication Outcomes Over Time

```{r}
#| label: fig-outcomes-time
#| fig-cap: "Replication outcomes by publication year of the original study."
#| eval: !expr data_available

flora |>
  filter(type == "replication", !is.na(outcome), !is.na(year_o)) |>
  count(year_o, outcome) |>
  ggplot(aes(x = year_o, y = n, fill = outcome)) +
  geom_col() +
  labs(x = "Original publication year", y = "Number of entries", fill = "Outcome") +
  theme_minimal()
```

## Reproduction Attempts

### Computational Success

*To be written.*

### Robustness

*To be written.*

## Cross-Disciplinary Comparisons

*To be written.*

{{< include sections/discussion.md >}}

{{< include sections/limitations.md >}}

{{< include sections/conclusion.md >}}

{{< include sections/social-responsibility.md >}}

{{< include sections/acknowledgments.md >}}

{{< include sections/funding.md >}}

# References {#sec-references .unnumbered}

::: {#refs}
:::
