---
title: "The FORRT Library of Reproduction and Replication Attempts: Documenting the Reproducibility and Replicability of the Sciences and Humanities"
author:
  - name: "Lukas Röseler"
    orcid: "0000-0002-6446-1901"
    affiliations:
      - name: "Münster Center for Open Science, University of Münster"
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    number-sections: false
    theme: cosmo
    css: styles.css
    fig-cap-location: bottom
    tbl-cap-location: top
    code-fold: true
    code-tools: false
    embed-resources: false
    citations-hover: true
    crossrefs-hover: true
    link-external-newwindow: true
  typst:
    output-file: "FLoRA-report"
    toc: false
    papersize: a4
    fig-cap-location: bottom
    tbl-cap-location: top
bibliography: references.bib
csl: apa.csl
link-citations: true
nocite: |
  @wallrich2026flora, @roseler2024replication, @roseler2025r2editorial
abstract: |
  In the sciences and humanities, repeatability of studies via reproduction (retesting with the same data) or replication (retesting with new data) is critical for affirming the correctness and generalizability of findings. While the rate of replications has strongly increased over the last decade, individual replications have been difficult to find due to them being buried in large-scale projects, published in journals other than those that published the original finding, or only published on preprint servers. To support identification of replications, we present the FORRT Library of Reproduction and Replication Attempts, a successor to the Replication Database (Röseler et al., 2024) that currently includes over 2,000 pairs of original and replication studies. We present our methods that led us to the current version,help us achieve our goal of a comprehensive database, share exploratory results, provide brief tutorials on tools that help researchers keep track of replications, and suggest ways for researchers to contribute studies. 
execute:
  echo: false
  warning: false
  message: false
  cache: false
---

::: {.content-visible when-format="html"}
<div class="wip-ribbon"><span>Work in Progress</span></div>
:::

```{r}
#| label: render-date
#| include: false
render_date <- format(Sys.Date(), "%d %B %Y")
```

::: {.content-visible when-format="html"}
**Snapshot rendered on `r render_date`.**
[📄 Download as PDF](FLoRA-report.pdf){.flora-pdf-btn}
:::

::: {.content-visible when-format="typst"}
*This PDF was generated on `r render_date` from the live FLoRA snapshot.*
:::


```{r setup}
#| include: false

library(tidyverse)
library(knitr)
library(here)

flora_path <- here::here("data", "flora.csv")

if (file.exists(flora_path)) {
  flora <- readr::read_csv(flora_path, show_col_types = FALSE, na = c("", "NA"))
  data_available <- TRUE
} else {
  flora <- tibble()
  data_available <- FALSE
}

report_date <- format(Sys.Date(), "%B %d, %Y")
n_entries   <- nrow(flora)
```


::: {.flora-box}
**Keywords:** replication, reproduction, meta-science, open science, FLoRA, FORRT
:::

::: {.flora-box}
### Lay Summary {.box-title}

{{< include sections/lay-summary.md >}}
:::

::: {.flora-box}
### Citation {.box-title}

Please cite this report as:

Röseler, L. (`r format(Sys.Date(), "%Y")`). *The FORRT Library of Reproduction
and Replication Attempts: Documenting the Reproducibility and Replicability of
the Sciences and Humanities.* <https://lukasroeseler.github.io/florareport/>

And cite the underlying dataset as @wallrich2026flora.
:::

::: {.callout-note appearance="simple"}
This report is automatically updated daily at 07:00 CEST using the most recent
version of the FLoRA dataset. Last build: **`r format(Sys.time(), "%Y-%m-%d %H:%M %Z")`**.
`r if (data_available) paste0("Current snapshot: **", scales::comma(n_entries), " entries**.") else "⚠ Data file not found — plots and tables are skipped in this build."`
:::

<!-- ============================================================= -->
<!-- PROSE SECTIONS — edit the .md files in sections/, not here.    -->
<!-- ============================================================= -->

{{< include sections/theory.md >}}

{{< include sections/methods.md >}}

{{< include sections/results.qmd >}}

{{< include sections/discussion.md >}}

{{< include sections/limitations.md >}}

{{< include sections/conclusion.md >}}

{{< include sections/social-responsibility.md >}}

{{< include sections/acknowledgments.md >}}

{{< include sections/funding.md >}}

# References {#sec-references .unnumbered}

::: {#refs}
:::
