---
title: "The FORRT Library of Reproduction and Replication Attempts: Documenting the Reproducibility and Replicability of the Sciences and Humanities"
author:
  - name: "Author Name"
    orcid: "0000-0000-0000-0000"
    affiliations:
      - name: "Affiliation"
date: today
date-format: "YYYY-MM-DD"
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    number-sections: true
    theme: cosmo
    css: styles.css
    fig-cap-location: bottom
    tbl-cap-location: top
    code-fold: true
    code-tools: true
    embed-resources: false
    citations-hover: true
    crossrefs-hover: true
    link-external-newwindow: true
bibliography: references.bib
csl: apa.csl
link-citations: true
nocite: |
  @wallrich2026flora, @roseler2024replication, @roseler2025r2editorial
abstract: |
  *To be written.* This abstract will summarize the report's aims, methods, key
  findings, and contributions to open science.
keywords:
  - replication
  - reproduction
  - meta-science
  - open science
  - FLoRA
  - FORRT
execute:
  echo: false
  warning: false
  message: false
  cache: false
---

```{r setup}
#| include: false

library(tidyverse)
library(knitr)
library(here)

# ---------- Load FLoRA data (fail gracefully) ----------
flora_path <- here::here("data", "flora.csv")

if (file.exists(flora_path)) {
  flora <- readr::read_csv(flora_path, show_col_types = FALSE, na = c("", "NA"))
  data_available <- TRUE
} else {
  flora <- tibble()
  data_available <- FALSE
}

report_date <- format(Sys.Date(), "%B %d, %Y")
n_entries   <- nrow(flora)
```

::: {.callout-note appearance="simple"}
This report is automatically updated daily at 07:00 CEST using the most recent version of the FLoRA dataset. Last build: **`r format(Sys.time(), "%Y-%m-%d %H:%M %Z")`**. `r if (data_available) paste0("Current snapshot: **", scales::comma(n_entries), " entries**.") else "⚠ Data file not found — plots and tables are skipped in this build."`
:::

# Lay Summary {#sec-lay-summary .unnumbered}

*To be written.* A plain-language summary (\~150–250 words) explaining what FLoRA is, why it matters, and what this report contributes.

# Citation {#sec-citation .unnumbered}

Please cite this report as:

> \[Author\]. (`r format(Sys.Date(), "%Y")`). *The FORRT Library of Reproduction and Replication Attempts: Documenting the Reproducibility and Replicability of the Sciences and Humanities.* \[URL\]

And cite the underlying dataset as @wallrich2026flora.

# Theory {#sec-theory}

*To be written.* Background and conceptual framing covering the replication and reproduction crises, why a comprehensive library matters, and the relationship between FLoRA and previous tracking efforts such as FReD [@roseler2024replication].

## The Replication and Reproduction Crises

*To be written.* Overview of the replication crisis in psychology [@osc2015reproducibility; @camerer2016economics] and the broader credibility revolution [@vazire2018credibility; @korbmacher2023replication].

## From FReD to FLoRA

*To be written.* How the FORRT Replication Database (FReD) evolved into FLoRA, expanding scope beyond psychology and adding reproductions as a tracked category.

## Defining Replications and Reproductions

*To be written.* Definitions following @parsons2022glossary and the FLoRA inclusion criteria: replications collect new data; reproductions re-analyse the original data.

# Methods {#sec-methods}

*To be written.* How the FLoRA dataset is constructed and how this report processes it.

## Inclusion Criteria

*To be written.* Studies must self-identify as a replication or reproduction, identify a specific target study, and replicate a study or experiment (not just a single association).

## Coding of Outcomes

### Replication Outcomes

*To be written.* Outcomes are coded as **Successful**, **Failed**, or **Mixed** based on how the replication authors characterise their results.

### Reproduction Outcomes

*To be written.* Reproductions are coded along two dimensions: computational success (Computationally Successful vs. Computational Issues) and robustness (Robust, Robustness Challenges, or Robustness Not Checked).

## Data Sources and Contributions

*To be written.* Description of how entries enter FLoRA — community submissions, large-scale projects, systematic searches.

## Data Pipeline for This Report

*To be written.* This report is rendered via a GitHub Actions workflow that downloads the latest `flora.csv` from the [FReD-data repository](https://github.com/forrtproject/FReD-data) daily at 07:00 CEST and rebuilds this page. All code is open and reproducible.

# Results {#sec-results}

*To be written.* Descriptive statistics and visualisations of the current FLoRA snapshot.

## Overview of the Current Database

```{r}
#| label: tbl-overview
#| tbl-cap: "Overview of the current FLoRA snapshot."
#| eval: !expr data_available

flora_summary <- flora |>
  summarise(
    `Total entries`              = n(),
    `Unique original studies`    = n_distinct(doi_o, na.rm = TRUE),
    `Unique replication studies`  = n_distinct(doi_r, na.rm = TRUE),
    Replications                 = sum(type == "replication", na.rm = TRUE),
    Reproductions                = sum(type == "reproduction", na.rm = TRUE)
  ) |>
  pivot_longer(everything(), names_to = "Category", values_to = "Count")

knitr::kable(flora_summary, format = "html")
```

## Replication Attempts

### Replications Across Disciplines

*To be written.*

### Replication Outcomes Over Time

```{r}
#| label: fig-outcomes-time
#| fig-cap: "Replication outcomes by publication year of the original study."
#| eval: !expr data_available

flora |>
  filter(type == "replication", !is.na(outcome), !is.na(year_o)) |>
  count(year_o, outcome) |>
  ggplot(aes(x = year_o, y = n, fill = outcome)) +
  geom_col() +
  labs(x = "Original publication year", y = "Number of entries", fill = "Outcome") +
  theme_minimal()
```

## Reproduction Attempts

### Computational Success

*To be written.*

### Robustness

*To be written.*

## Cross-Disciplinary Comparisons

*To be written.*

# Discussion {#sec-discussion}

*To be written.* Interpretation of the descriptive findings and their implications.

## Patterns in Replicability

*To be written.*

## Patterns in Reproducibility

*To be written.*

## Implications for Researchers, Educators, and Policy

*To be written.*

# Limitations {#sec-limitations}

*To be written.* Honest treatment of caveats, including crowdsourced data quality, coverage biases across disciplines, the self-identification requirement, and the absence of statistical effect sizes (in contrast to FReD).

# Conclusion {#sec-conclusion}

*To be written.* A concise wrap-up: what FLoRA contributes, where the project is heading, and how to engage.

# Social Responsibility {#sec-social-responsibility .unnumbered}

*To be written.* Statement on the open, community-driven, equitable nature of FLoRA.

# Acknowledgments {#sec-acknowledgments .unnumbered}

*To be written.* Thanks to the FLoRA contributors, FORRT community, and supporting institutions.

# Funding {#sec-funding .unnumbered}

*To be written.*

# References {#sec-references .unnumbered}

::: {#refs}
:::
