---
title: "The FORRT Library of Reproduction and Replication Attempts: Documenting the Reproducibility and Replicability of the Sciences and Humanities"
author:
  - name: "Author Name"
    orcid: "0000-0000-0000-0000"
    affiliations:
      - name: "Affiliation"
date: today
date-format: "YYYY-MM-DD"
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    number-sections: true
    theme: cosmo
    css: styles.css
    fig-cap-location: bottom
    tbl-cap-location: top
    code-fold: true
    code-tools: true
    embed-resources: false
    citations-hover: true
    crossrefs-hover: true
    link-external-newwindow: true
  pdf:
    documentclass: article
    papersize: a4
    fontsize: 11pt
    geometry:
      - margin=1in
    toc: true
    number-sections: true
    fig-cap-location: bottom
    tbl-cap-location: top
bibliography: references.bib
csl: apa.csl
link-citations: true
abstract: |
  *To be written.* This is the abstract section that will summarize the report's
  aims, methods, key findings, and contributions to open science.
keywords:
  - replication
  - reproduction
  - meta-science
  - open science
  - FLoRA
  - FORRT
execute:
  echo: false
  warning: false
  message: false
  cache: false
---

```{r setup}
#| include: false

# Packages
library(tidyverse)
library(knitr)
library(kableExtra)
library(here)

# Load the most recent FLoRA data
flora <- readr::read_csv(here::here("data", "flora.csv"), show_col_types = FALSE)

# Date stamp for the report
report_date <- format(Sys.Date(), "%B %d, %Y")
```

::: {.callout-note appearance="simple"}
This report is automatically updated daily at 07:00 CEST using the most recent version of the FLoRA dataset. Last build: `r format(Sys.time(), "%Y-%m-%d %H:%M %Z")`.
:::

# Lay Summary {#sec-lay-summary .unnumbered}

```{=html}
<!-- A plain-language summary written for a general audience, ~150-250 words.
     Avoid jargon. Explain what FLoRA is, why it matters, and what this report
     contributes. -->
```

# Citation {#sec-citation .unnumbered}

<!-- Recommended citation for this report. Include version/date and DOI when available. -->

# Theory {#sec-theory}

```{=html}
<!-- Background and conceptual framing.
     - The replication and reproduction crises across disciplines
     - Why a comprehensive library matters
     - Distinction between replication and reproduction (per FLoRA definitions)
     - Relationship to FReD and prior tracking efforts
     - Theoretical contribution of meta-scientific tracking -->
```

## The Replication and Reproduction Crises

## From FReD to FLoRA

## Defining Replications and Reproductions

# Methods {#sec-methods}

<!-- How the FLoRA dataset is constructed and how this report processes it. -->

## Inclusion Criteria

## Coding of Outcomes

### Replication Outcomes

### Reproduction Outcomes

## Data Sources and Contributions

## Data Pipeline for This Report

```{=html}
<!-- Describe the GitHub Actions workflow, the daily refresh, the source CSV,
     and the reproducibility of this report. -->
```

# Results {#sec-results}

<!-- Descriptive statistics and visualisations of the current FLoRA snapshot. -->

## Overview of the Current Database

```{r overview-table}
#| label: tbl-overview
#| tbl-cap: "Overview of the current FLoRA snapshot."
#| eval: false

# Placeholder summary table
```

## Replication Attempts

### Replications Across Disciplines

### Replication Outcomes Over Time

## Reproduction Attempts

### Computational Success

### Robustness

## Cross-Disciplinary Comparisons

# Discussion {#sec-discussion}

<!-- Interpretation of the findings and their implications. -->

## Patterns in Replicability

## Patterns in Reproducibility

## Implications for Researchers, Educators, and Policy

# Limitations {#sec-limitations}

```{=html}
<!-- Honest treatment of caveats:
     - Crowdsourced data quality
     - Coverage biases across disciplines
     - Definitional ambiguity in replication closeness
     - Self-identification requirement
     - No statistical effect sizes (in contrast to FReD) -->
```

# Conclusion {#sec-conclusion}

<!-- A concise wrap-up: what FLoRA contributes, where it's heading, how to engage. -->

# Social Responsibility {#sec-social-responsibility .unnumbered}

```{=html}
<!-- Statement on the open, community-driven, equitable nature of FLoRA.
     Inclusivity, accessibility, contribution pathways, recognition of contributors. -->
```

# Acknowledgments {#sec-acknowledgments .unnumbered}

<!-- Thank contributors, FORRT community, and supporting institutions. -->

# Funding {#sec-funding .unnumbered}

<!-- Funding statement. -->

# References {#sec-references .unnumbered}

::: {#refs}
:::
