# Results {#sec-results}

```{r}
#| label: setup-results
#| include: false
#| eval: !expr data_available

library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)

# Helper: render interactively in HTML (mouse-over only, no toolbar),
# statically otherwise
render_plot <- function(p, tooltip = "text") {
  if (knitr::is_html_output() && requireNamespace("plotly", quietly = TRUE)) {
    plotly::ggplotly(p, tooltip = tooltip) |>
      plotly::config(
        displayModeBar = FALSE,
        displaylogo    = FALSE,
        showTips       = FALSE
      ) |>
      plotly::layout(hoverlabel = list(bgcolor = "white"))
  } else {
    p
  }
}

# Consistent outcome ordering and colors
outcome_levels <- c("successful", "mixed", "failed", "inconclusive")
outcome_labels <- c("Successful", "Mixed", "Failed", "Inconclusive")
outcome_colors <- c(
  "Successful"   = "#4CB07A",
  "Mixed"        = "#E6A24C",
  "Failed"       = "#E2473B",
  "Inconclusive" = "#5A6B7B"
)

prep_outcomes <- function(df) {
  df |>
    filter(!is.na(outcome)) |>
    mutate(outcome = factor(
      tools::toTitleCase(tolower(outcome)),
      levels = outcome_labels
    )) |>
    filter(!is.na(outcome))
}
```

## Overview of the Current Database

-   State the date of the current snapshot (consider pulling this
    dynamically from the data file timestamp, e.g.,
    `format(file.info("data/flora.csv")$mtime, "%B %Y")`).
-   Walk the reader through @tbl-overview: total number of entries,
    share of replications vs. reproductions, ratio of unique original to
    unique replication studies (i.e., how often the same original study
    has been replicated multiple times).
-   Note any caveats about coverage (e.g., the database is
    non-exhaustive, English-language bias, dependence on
    self-identification as a replication).

```{r}
#| label: tbl-overview
#| tbl-cap: "Overview of the current FLoRA snapshot."
#| eval: !expr data_available

flora_summary <- flora |>
  summarise(
    `Total entries`              = n(),
    `Unique original studies`    = n_distinct(doi_o, na.rm = TRUE),
    `Unique replication studies` = n_distinct(doi_r, na.rm = TRUE),
    Replications                 = sum(type == "replication", na.rm = TRUE),
    Reproductions                = sum(type == "reproduction", na.rm = TRUE)
  ) |>
  pivot_longer(everything(), names_to = "Category", values_to = "Count")

knitr::kable(flora_summary, format = "html")
```

## Reproduction Attempts

-   Define what is meant by *reproduction* in FLoRA (re-running analyses
    on the same data, distinguishing computational reproducibility from
    robustness).
-   Mention the main sources of reproductions (Replication Network list,
    Institute for Replication reports).
-   Flag that, unlike replications, reproductions test the same data and
    so any failure points more directly to coding/analytic issues.

### Outcomes

-   Summarise @tbl-outcomes-reproduction in prose: total number of
    reproductions, share that were successful, share that failed, share
    that were mixed/inconclusive.
-   Refer the reader to @fig-outcome-distribution-reproduction for a
    visual overview.
-   Consider commenting on the (probable) low share of "inconclusive"
    outcomes and what that means in practice.

```{r}
#| label: tbl-outcomes-reproduction
#| tbl-cap: "Reproduction outcomes."
#| eval: !expr data_available

flora |>
  filter(type == "reproduction", !is.na(outcome)) |>
  count(outcome, name = "Frequency") |>
  filter(Frequency > 0) |>
  arrange(desc(Frequency)) |>
  rename(Outcome = outcome) |>
  knitr::kable(format = "html")
```

```{r}
#| label: fig-outcome-distribution-reproduction
#| fig-cap: "Distribution of reproduction outcomes."
#| eval: !expr data_available

repro_df <- flora |>
  filter(type == "reproduction") |>
  prep_outcomes() |>
  count(outcome) |>
  mutate(
    pct  = n / sum(n),
    text = paste0(outcome, ": ", n, " (", percent(pct, accuracy = 0.1), ")")
  )

p_repro_dist <- ggplot(repro_df,
                       aes(x = n, y = "Reproductions",
                           fill = outcome, text = text)) +
  geom_col(position = "stack", width = 0.5) +
  scale_fill_manual(values = outcome_colors, name = NULL) +
  scale_x_continuous(labels = label_number(big.mark = ",")) +
  labs(x = NULL, y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.grid.major.y = element_blank(),
        panel.grid.minor   = element_blank())

render_plot(p_repro_dist)
```

### Outcomes Over Time (Original Study Year)

-   Describe the temporal coverage: which decade(s) the original studies
    span, and where the bulk of reproduced studies are concentrated.
-   Comment on whether older or more recent original studies tend to
    reproduce better — keeping in mind selection effects (newer studies
    are more likely to share data, older studies less likely to be
    picked for reproduction).

```{r}
#| label: fig-repro-outcomes-year-o
#| fig-cap: "Reproduction outcomes by publication year of the original study."
#| eval: !expr data_available

p <- flora |>
  filter(type == "reproduction", !is.na(year_o)) |>
  prep_outcomes() |>
  count(year_o, outcome) |>
  mutate(text = paste0("Year: ", year_o, "<br>",
                       outcome, ": ", n)) |>
  ggplot(aes(x = year_o, y = n, fill = outcome, text = text)) +
  geom_col() +
  scale_fill_manual(values = outcome_colors, name = "Outcome") +
  labs(x = "Original publication year", y = "Number of entries") +
  theme_minimal()

render_plot(p)
```

### Outcomes Over Time (Reproduction Study Year)

-   Describe how the volume of reproduction attempts has evolved over
    time (likely a sharp rise after the launch of I4R and similar
    initiatives).
-   Note whether the share of failed/mixed reproductions has changed in
    recent years (e.g., as reporting standards tighten or as more
    journals adopt data-sharing policies).

```{r}
#| label: fig-repro-outcomes-year-r
#| fig-cap: "Reproduction outcomes by publication year of the reproduction study."
#| eval: !expr data_available

p <- flora |>
  filter(type == "reproduction", !is.na(year_r)) |>
  prep_outcomes() |>
  count(year_r, outcome) |>
  mutate(text = paste0("Year: ", year_r, "<br>",
                       outcome, ": ", n)) |>
  ggplot(aes(x = year_r, y = n, fill = outcome, text = text)) +
  geom_col() +
  scale_fill_manual(values = outcome_colors, name = "Outcome") +
  labs(x = "Reproduction publication year", y = "Number of entries") +
  theme_minimal()

render_plot(p)
```

### Outcomes by Original Journal

-   Highlight which original-study journals are most frequently targeted
    for reproductions (likely top economics/political science journals
    if I4R is the main source).
-   Compare success rates across journals, but caution against
    over-interpreting differences given small per-journal sample sizes.
-   Mention that the figure shows the top 15 journals only and that the
    full breakdown is available in the database.

```{r}
#| label: fig-repro-outcomes-journal-o
#| fig-cap: "Reproduction outcomes by journal of the original study (top 15 journals)."
#| eval: !expr data_available

top_journals <- flora |>
  filter(type == "reproduction", !is.na(journal_o)) |>
  count(journal_o, sort = TRUE) |>
  slice_head(n = 15) |>
  pull(journal_o)

p <- flora |>
  filter(type == "reproduction", journal_o %in% top_journals) |>
  prep_outcomes() |>
  count(journal_o, outcome) |>
  mutate(text = paste0(journal_o, "<br>", outcome, ": ", n)) |>
  ggplot(aes(x = n,
             y = reorder(journal_o, n, sum),
             fill = outcome, text = text)) +
  geom_col() +
  scale_fill_manual(values = outcome_colors, name = "Outcome") +
  labs(x = "Number of entries", y = NULL) +
  theme_minimal()

render_plot(p)
```

### Outcomes by Reproduction Journal

-   Identify the outlets that publish most reproduction reports (e.g.,
    I4R reports, *Journal of Comments and Replications in Economics*,
    etc.).
-   Briefly discuss how concentrated or dispersed the publishing
    landscape for reproductions is.

```{r}
#| label: fig-repro-outcomes-journal-r
#| fig-cap: "Reproduction outcomes by journal of the reproduction study (top 15 journals)."
#| eval: !expr data_available

top_journals_r <- flora |>
  filter(type == "reproduction", !is.na(journal_r)) |>
  count(journal_r, sort = TRUE) |>
  slice_head(n = 15) |>
  pull(journal_r)

p <- flora |>
  filter(type == "reproduction", journal_r %in% top_journals_r) |>
  prep_outcomes() |>
  count(journal_r, outcome) |>
  mutate(text = paste0(journal_r, "<br>", outcome, ": ", n)) |>
  ggplot(aes(x = n,
             y = reorder(journal_r, n, sum),
             fill = outcome, text = text)) +
  geom_col() +
  scale_fill_manual(values = outcome_colors, name = "Outcome") +
  labs(x = "Number of entries", y = NULL) +
  theme_minimal()

render_plot(p)
```

## Replication Attempts

-   Define *replication* as used in FLoRA (new data collection, ranging
    from close/direct to conceptual; self-identified as a replication).
-   Note the main source (FReD, supplemented by OpenAlex search) and the
    inclusion criteria (e.g., must self-identify, must target a specific
    original study).
-   Briefly contrast with reproductions to set up the section.
-   

### Outcomes

-   Summarise @tbl-outcomes-replication: total replications, share
    successful, mixed, failed, inconclusive.
-   Refer to @fig-outcome-distribution-replication and compare the
    distribution to the one for reproductions (likely a higher failure
    rate).
-   Discuss possible reasons for the failure rate (publication bias
    toward "interesting" — i.e., failed — replications, methodological
    differences in conceptual replications, lower power in original
    studies).

```{r}
#| label: tbl-outcomes-replication
#| tbl-cap: "Replication outcomes."
#| eval: !expr data_available

flora |>
  filter(type == "replication", !is.na(outcome)) |>
  count(outcome, name = "Frequency") |>
  filter(Frequency > 0) |>
  arrange(desc(Frequency)) |>
  rename(Outcome = outcome) |>
  knitr::kable(format = "html")
```

```{r}
#| label: fig-outcome-distribution-replication
#| fig-cap: "Distribution of replication outcomes."
#| eval: !expr data_available

repl_df <- flora |>
  filter(type == "replication") |>
  prep_outcomes() |>
  count(outcome) |>
  mutate(
    pct  = n / sum(n),
    text = paste0(outcome, ": ", n, " (", percent(pct, accuracy = 0.1), ")")
  )

p_repl_dist <- ggplot(repl_df,
                      aes(x = n, y = "Replications",
                          fill = outcome, text = text)) +
  geom_col(position = "stack", width = 0.5) +
  scale_fill_manual(values = outcome_colors, name = NULL) +
  scale_x_continuous(labels = label_number(big.mark = ",")) +
  labs(x = NULL, y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.grid.major.y = element_blank(),
        panel.grid.minor   = element_blank())

render_plot(p_repl_dist)
```

### Outcomes Over Time (Original Study Year)

-   Describe the temporal range of the original studies that have been
    replicated and where the bulk lies (probably 1990s–2010s).
-   Comment on any visible trend in success rates by original-study year
    (e.g., are pre-2011 "replication crisis" studies replicating less
    well than more recent ones?).

```{r}
#| label: fig-repl-outcomes-year-o
#| fig-cap: "Replication outcomes by publication year of the original study."
#| eval: !expr data_available

p <- flora |>
  filter(type == "replication", !is.na(year_o)) |>
  prep_outcomes() |>
  count(year_o, outcome) |>
  mutate(text = paste0("Year: ", year_o, "<br>",
                       outcome, ": ", n)) |>
  ggplot(aes(x = year_o, y = n, fill = outcome, text = text)) +
  geom_col() +
  scale_fill_manual(values = outcome_colors, name = "Outcome") +
  labs(x = "Original publication year", y = "Number of entries") +
  theme_minimal()

render_plot(p)
```

### Outcomes Over Time (Replication Study Year)

-   Describe the rise of replication activity over time, likely with a
    clear post-2015 surge driven by RP:P, ManyLabs, RRR, and related
    projects.
-   Comment on whether the share of successful replications has changed
    over time — improvements may reflect better methods
    (preregistration, larger samples) and/or shifting selection of which
    originals get replicated.

```{r}
#| label: fig-repl-outcomes-year-r
#| fig-cap: "Replication outcomes by publication year of the replication study."
#| eval: !expr data_available

p <- flora |>
  filter(type == "replication", !is.na(year_r)) |>
  prep_outcomes() |>
  count(year_r, outcome) |>
  mutate(text = paste0("Year: ", year_r, "<br>",
                       outcome, ": ", n)) |>
  ggplot(aes(x = year_r, y = n, fill = outcome, text = text)) +
  geom_col() +
  scale_fill_manual(values = outcome_colors, name = "Outcome") +
  labs(x = "Replication publication year", y = "Number of entries") +
  theme_minimal()

render_plot(p)
```

### Outcomes by Original Journal

-   Note which original-study journals dominate the replication record
    (likely *Psychological Science*, *JPSP*, *PNAS*, *Science*, etc.).
-   Compare success rates across these journals — but caveat that this
    reflects which findings were *selected* for replication, not journal
    quality per se.

```{r}
#| label: fig-repl-outcomes-journal-o
#| fig-cap: "Replication outcomes by journal of the original study (top 15 journals)."
#| eval: !expr data_available

top_journals <- flora |>
  filter(type == "replication", !is.na(journal_o)) |>
  count(journal_o, sort = TRUE) |>
  slice_head(n = 15) |>
  pull(journal_o)

p <- flora |>
  filter(type == "replication", journal_o %in% top_journals) |>
  prep_outcomes() |>
  count(journal_o, outcome) |>
  mutate(text = paste0(journal_o, "<br>", outcome, ": ", n)) |>
  ggplot(aes(x = n,
             y = reorder(journal_o, n, sum),
             fill = outcome, text = text)) +
  geom_col() +
  scale_fill_manual(values = outcome_colors, name = "Outcome") +
  labs(x = "Number of entries", y = NULL) +
  theme_minimal()

render_plot(p)
```

### Outcomes by Replication Journal

-   Identify the outlets that publish most replications (e.g.,
    *Collabra: Psychology*, *SPPS*, *Royal Society Open Science*,
    *Meta-Psychology*, *AMPPS*).
-   Comment on whether replication-friendly journals show a different
    mix of outcomes than mainstream journals — this can hint at whether
    there is publication bias against null replications.

```{r}
#| label: fig-repl-outcomes-journal-r
#| fig-cap: "Replication outcomes by journal of the replication study (top 15 journals)."
#| eval: !expr data_available

top_journals_r <- flora |>
  filter(type == "replication", !is.na(journal_r)) |>
  count(journal_r, sort = TRUE) |>
  slice_head(n = 15) |>
  pull(journal_r)

p <- flora |>
  filter(type == "replication", journal_r %in% top_journals_r) |>
  prep_outcomes() |>
  count(journal_r, outcome) |>
  mutate(text = paste0(journal_r, "<br>", outcome, ": ", n)) |>
  ggplot(aes(x = n,
             y = reorder(journal_r, n, sum),
             fill = outcome, text = text)) +
  geom_col() +
  scale_fill_manual(values = outcome_colors, name = "Outcome") +
  labs(x = "Number of entries", y = NULL) +
  theme_minimal()

render_plot(p)
```

## Summary

-   Pull together the headline numbers: how many replications, how many
    reproductions, what share of each was successful.
-   Highlight 1–2 of the most striking findings from the figures above
    (e.g., growth over time, concentration in a few journals,
    differences between replications and reproductions).
-   Briefly point forward to the discussion section.
